Title

### 2023-08-15 paper/paper.tex
paper

\onecolumn
\begin{table}[h]
\centering
\begin{tabular}{|l c c|} 
    \hline
    Name & input length & embedding dimension  \\ 
    \hline
    embedding reproduction (rep)\cite{yang2018learned}       & 64    & 64    \\
    dnabert \cite{ji2021dnabert}                     & 512     & 768  \\
    prose   \cite{bepler2021learning}                   & 512   & 100    \\
    alphafold  \cite{jumper2021highly}                 & 1024   & 384 \\
    evolutionary scale modeling (esm2) \cite{lin2022language}   & 1024    & 1280 \\  
    \hline
\end{tabular}
\caption{Embedders used in the experiments.}
\label{table:data}
\end{table}
\twocolumn

>>>>

In this section we describe the pipeline used to analyze the embeddings. As shown in Table \ref{table:data}, the input length is different between the models as well as the output produced. We want to address the following problems: 1) compare different methods to join togheter the amminoacid-specific contextual representations in order to have a representation for the whole chunk; 2) compare different methods to join togheter the representations of the chunks in order to have a representation for the whole protein; 3) find out if these representations reflect known properties of the proteins.

\subsection{Single amminoacid contextual representation}

\onecolumn
\begin{table}[h]
\centering
\begin{tabular}{|l c c|} 
    \hline
    Name & input length (chunk) & embedding dimension  \\ 
    \hline
    embedding reproduction (rep)\cite{yang2018learned}       & 64    & 64 per chunk   \\
    dnabert \cite{ji2021dnabert}                     & 512     & 768 per chunk \\
    prose   \cite{bepler2021learning}                   & 512   & 100 per amino acid   \\
    alphafold  \cite{jumper2021highly}                 & 1024   & 384 per ammino acid\\
    evolutionary scale modeling (esm2) \cite{lin2022language}   & 1024    & 1280 per ammino acid \\  
    \hline
\end{tabular}
\caption{Embedders used in the experiments.}
\label{table:data}
\end{table}
\twocolumn
